SimTrans: A Self-supervised Method for Biomedical Image Segmentation

### 2023-06-13 cvpr_latex/PaperForReview.tex
add title and authors

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Author Guidelines for \confName~Proceedings}

\author{Shenfan Wang\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Zhen Zhou\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
\and
Jiabei Chen\\
Institution3\\
Institution3 address\\
{\tt\small thirdauthor@i3.org}
\and
Changyong Li\\
Institution4\\
Institution4 address\\
{\tt\small forthauthor@i4.org}
}
\maketitle

>>>>

%%%%%%%%% TITLE - PLEASE UPDATE
% \title{\LaTeX\ Author Guidelines for \confName~Proceedings}
\title{SimTrans: A Self-supervised Method for Biomedical Image Segmentation}

\author{Shengfan Wang\\
CSBIO\\
SEIEE 2-306\\
{\tt\small diofan0814@sjtu.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Zhen Zhou\\
CSBIO\\
SEIEE 2-306\\
{\tt\small zz20020101@sjtu.edu.cn}
\and
Jiabei Cheng\\
CSBIO\\
SEIEE 2-306\\
{\tt\small jiabei\_cheng@sjtu.edu.cn}
\and
Changyong Li\\
CSBIO\\
SEIEE 2-306\\
{\tt\small steven\_li@sjtu.edu.cn}
}
\maketitle
